`r paste('#', basename(filelist[[i]]), '{data-navmenu="TDReport Filename"}')`

`r htmltools::tags$h3(basename(filelist[[i]]), style="text-align:center;color:#ffffff")`

```{r setup, include=FALSE}

# knitr::opts_knit$set(base.dir = normalizePath(tempdir(), winslash = '/'))

library(flexdashboard)
library(shiny)
library(shinydashboard)
library(magrittr)
library(stringr)
library(forcats)
library(purrr)
library(UpSetR)
library(ggplot2)
library(DT)
library(plotly)
library(ggthemes)
library(viridis)
library(waffle)
library(dplyr)
library(magick)
library(xfun)
library(htmltools)
library(mime)

# Plotly parameters

download_button_params <- 
  list(
    format = "svg",
    width = 800,
    height = 500
  )

# ggplot themes

col_plot_theme <- 
  list(
    theme_minimal(),
    theme(
      axis.text.x = element_text(angle = 90),
      panel.grid.major.x = element_blank()
    )
  )

heatmap_theme <- 
  list(
    theme_minimal(),
    theme(
      text = element_text(size=16)
    ) 
  )

# Find newest file function

find_newest_file <-
  function(
    path
  ) {
    purrr::map_chr(
      path,
      ~fs::dir_info(.x) %>%
        dplyr::filter(modification_time == max(modification_time)) %>%
        dplyr::pull("path")
    )
  }

```

Row {.tabset .tabset-fade data-height=175}
-------------------------------------

### Identifications Tables

In a static GUPPI report, embedded protein and proteoform results can be downloaded in .xlsx format using the following links:

```{r}

xfun::embed_file(
  find_newest_file(
    fs::path(
      outputdir,
      "protein_results"
    )
  ),
  text = "Download protein results"
)

```

```{r}

xfun::embed_file(
  find_newest_file(
    fs::path(
      outputdir,
      "proteoform_results"
    )
  ),
  text = "Download proteoform results"
)

```



Row {.tabset .tabset-fade}
-------------------------------------

### Protein Counts by Fraction

```{r, out.width = "100%", dpi = 300}

results_protein[[i]] %>% 
  group_by(fraction) %>% 
  summarise("protein count" = n()) %>%
  ggplot() +
  geom_col(
    aes(fraction, `protein count`),
    color = "black",
    fill = "#4C4184",
    size = 0.25
  ) +
  labs(
    x = "Fraction",
    y = "Protein Count"
  ) +
  col_plot_theme


```

### Protein Counts by Filename

``` {r}

results_protein[[i]] %>% 
  group_by(filename) %>% 
  summarise("protein count" = n()) %>%
  mutate(filename = sub('(^[^_]+_[^_]+_[^_]+)_(.*)$', '\\1_ \\2', filename)) %>% 
  # mutate(filename = stringr::str_trunc(filename, 40, side = "left")) %>%
  ggplot() +
  geom_col(
    aes(filename, `protein count`),
    color = "black",
    fill = "#4C4184",
    size = 0.25
  ) +
  labs(
    x = "Filename",
    y = "Protein Count"
  ) +
  guides(
    color = "none",
    fill = "none"
  ) +
  scale_x_discrete(labels = function(x) stringr::str_wrap(x, width = 8)) +
  col_plot_theme


```


Row
-------------------------------------

### Proteoform Identifications, UpSet Plot

```{r dpi=300, echo=FALSE}

fraction_number <- 
  results_protein_allhits[[i]] %>% 
  dplyr::pull(
    fraction
  ) %>% 
  unique() %>% 
  length()

if (fraction_number > 1) {
  results_protein_allhits[[i]] %>% 
    dplyr::select(
      ProteoformRecordNum,
      fraction
    ) %>%
    dplyr::arrange(fraction) %>%
    tidyr::pivot_wider(
      names_from = fraction,
      values_from =
        "ProteoformRecordNum",
      values_fn = list,
      names_prefix = "Frac_"
    ) %>%
    purrr::flatten() %>%
    list() %>%
    rlang::set_names("1") %>% 
    viztools::make_UpSet_plot()
} else {
  
  pander::pander("Only one fraction, no UpSet plot made") 
  
}

```


### Proteoform Identifications, Intersection Degree Plot

```{r}

results_protein_allhits[[i]] %>% 
  dplyr::select(
    ProteoformRecordNum,
    fraction
  ) %>%
  dplyr::arrange(fraction) %>%
  tidyr::pivot_wider(
    names_from = fraction,
    values_from =
      ProteoformRecordNum,
    values_fn = list,
    names_prefix = "Frac_"
  ) %>%
  purrr::flatten() %>%
  purrr::map(unique) %>% 
  viztools::make_intersection_degree_plot(
    Yrange = c(0, 100),
    plotType = "Proteoform"
  )

```

Row {data-height=500}
-------------------------------------

### Proteoform Identifications, Heatmap (Bin size = 1 kDa)

```{r}

results_protein_allhits[[i]] %>% 
  dplyr::group_by(
    ProteoformRecordNum,
    fraction
  ) %>% 
  viztools::make_heatmap(
    plotType = "Proteoform",
    orientation = "v",
    binSize = 1000,
    massColname = "ObservedPrecursorMass",
    fractionColname = "fraction"
  )

```

### Proteoform Identifications Heatmap, Result Sets (Bin size = 1 kDa)

```{r}

results_proteoform[[i]] %>% 
  dplyr::mutate(ResultSet = stringr::str_wrap(ResultSet,10)) %>%
  ggplot(aes(ObservedPrecursorMass/1000, ResultSet)) +
  geom_bin2d(aes(group = ResultSet), position = "identity", stat = "bin2d") +
  scale_fill_viridis_c(option = "C", direction = -1) +
  labs(
    x = "Mass Bin (kDa)",
    y = "Result Set"
  ) +
  theme_minimal() +
  theme(text = ggplot2::element_text(size=18))



```

Row
-------------------------------------

### Protein Identifications, Waffle Plot

```{r echo=FALSE, message=FALSE, out.width="100%"}

waffle1 <- 
  results_protein_countsbyfraction %>%
  dplyr::filter(tdreport_name == basename(filelist[[i]])) %>%
  dplyr::ungroup() %>% 
  dplyr::select(-tdreport_name) %>% 
  viztools::waffle_iron(
    fraction_colname = "fraction"
  )

fig1 <- image_graph(height = 2400, width = 3200, res = 300)

waffle1

dev.off()

magick::image_trim(fig1)


```

Row
-------------------------------------

### Hit Count vs. Intact Monoisotopic Mass, Linear Scale

```{r}

allhits_sum <- 
  results_protein_allhits[[i]] %>% 
  mutate(MonoisotopicMass = MonoisotopicMass/1000) %>% 
  dplyr::rename(`MonoisotopicMass (kDa)` = MonoisotopicMass) %>% 
  group_by(
    AccessionNumber,
    `MonoisotopicMass (kDa)`
  ) %>% 
  summarize(`Hit Count` = n()) %>% 
  ungroup()

allhits_sum %>% 
  ggplot(aes(`MonoisotopicMass (kDa)`, `Hit Count`)) +
  geom_point(size = 1) +
  labs(
    x = "Intact Monoisotopic Mass (kDa)",
    y = "Hit Count"
  ) +
  scale_x_continuous(
    breaks = scales::pretty_breaks()
  ) +
  scale_size_identity() +
  theme_minimal() +
  theme(
    panel.background = element_blank(),
    panel.grid.major.x = element_blank(),
    panel.grid.minor.x = element_blank(),
    axis.line = element_line(color = "black"),
    axis.ticks = element_line(color = "black"),
    text = element_text(size = 12)
  )


```

### Hit Count vs. Intact Monoisotopic Mass, Log10 Scale

```{r}

allhits_sum %>% 
  ggplot(aes(`MonoisotopicMass (kDa)`, log10(`Hit Count`))) +
  geom_point(size = 1) +
  labs(
    x = "Intact Monoisotopic Mass (kDa)",
    y = "Log10(Hit Count)"
  ) +
  scale_x_continuous(
    breaks = scales::pretty_breaks()
  ) +
  scale_size_identity() +
  theme_minimal() +
  theme(
    panel.background = element_blank(),
    panel.grid.major.x = element_blank(),
    panel.grid.minor.x = element_blank(),
    axis.line = element_line(color = "black"),
    axis.ticks = element_line(color = "black"),
    text = element_text(size = 12)
  )

```


Row
-------------------------------------

### -log10(Q-value) vs. Intact Monoisotopic Mass

```{r, out.width = "100%", dpi = 300}

allhits_qvals <- 
  results_proteoform[[i]] %>%
  mutate(MonoisotopicMass = MonoisotopicMass/1000) %>% 
  dplyr::rename(`MonoisotopicMass (kDa)` = MonoisotopicMass)

allhits_qvals %>% 
  ggplot(aes(`MonoisotopicMass (kDa)`, -log10(GlobalQvalue))) +
  geom_point(size = 1) +
  labs(
    x = "Intact Monoisotopic Mass (kDa)",
    y = "-Log10(Global Q-value)"
  ) +
  scale_x_continuous(
    breaks = scales::pretty_breaks()
  ) +
  scale_size_identity() +
  theme_minimal() +
  theme(
    panel.background = element_blank(),
    panel.grid.major.x = element_blank(),
    panel.grid.minor.x = element_blank(),
    axis.line = element_line(color = "black"),
    axis.ticks = element_line(color = "black"),
    text = element_text(size = 12)
  )

```

